\thispagestyle{abstractpagestyle}

\vspace*{36pt}

\begin{center}
    \textbf{\fontsize{20pt}{24pt} \selectfont ABSTRACT}
\end{center}

\vspace{24pt}

The home automation system based on the Arduino Mega development board incorporates several smart modules designed to enhance home efficiency. The temperature control system monitors and adjusts the temperature of the house by using a temperature sensor, a fan for cooling and a light bulb for heating. Users can set the desire ambient temperature via an integrated keyboard, thus providing a pleasant environment.

For safety assurance, the project includes a gas and smoke detection system with an alarm. This module is based on a buzzer to signal irregularities and a sensor to detect gas and smoke. The purpose of this system is to prevent fires and accidents caused by gas leakages.

The lighting system consists of leds that turn on upon detecting motion and according to the ambient light level. The photoresistor module detects the room's light level and adjusts the lighting, saving energy. Additionally, another led turns on automatically upon detecting motion, improving the home's accessibility and safety.

Another assembly of the project is an automatic door opening system, consisting of a servomotor and an ultrasonic sensor. The servomotor is controlled by the ultrasonic sensor, which sends a signal upon detecting people in the door's vicinity. This system facilitates access to the house and enhances the comfort level.

Data from the temperature and humidity sensor, the gas and smoke sensor, and the barometric pressure and altitude sensor are displayed on a LCD display, providing a local visualization of the monitored parameters.

The project facilitates parameter monitoring over various distances. For medium distances, a Bluetooth module sends the data to an Android application specifically implemented for this system. For long distances, a NodeMCU module with ESP8266 is used, enabling WiFi connection, so parameters can be viewed using the Blynk platform, both in desktop and mobile modes.

All these systems are integrated into a model built by me, demonstrating the functionality and efficiency of the home automation project.
%The English abstract will be on the third page of the manuscriptand will present synthetically the paper work. The maximum length of the abstract is one page written with Arial characters, size 12 pt. The abstract text will begin after two blank lines (size 12pt.) from the “ABSTRACT” title. Before title there will be left three blank lines of 12pt size.

\vfill